Make any stupid plot you want

### 2021-01-06 draft/sections/math.tex
q

\paragraph{Example: Translation}
According to Stevens, interval data jas general linear group actions \cite{stevensTheoryScalesMeasurement1946,leaFormalizationMeasurementScale}. Position is a visual variable that can support translation \cite{bertinIIPropertiesGraphic2011,krygierMakingMapsVisual2005,munznerMarksChannels}.

For example, here $\nu$ is a direct map $nu(e) = v$ and the transform function is a multiplicative shift $t(x) = x + x$ applied twice

\begin{align}
    \nu(t(t(e))) &= t_v(t(\nu(e)))\\
    \nu(t(e+e)) &= t(t_v(v))\\
    \nu((e+e) + (e+e)) &= t(v+v)\\
    \nu(4e) &= (v_v) + (v+v)\\
    \nu(4e)&=4v
\end{align}

Here $\nu$ is valid because scaling the data by a factor of 4 causes a scaling of the equivalent visualization by 4.

\paragraph{Example: Invalid $\nu$}
shifts in either space need to be mirrored in the other space, this is not valid  here's why:
\begin{equation}
    \label{eq:nu_equation_bad}
    \begin{tikzcd}
        E_1 \arrow[r] \arrow[r, "\lambda:e\mapsto.5"] \arrow[d, "e+2"'] & V_1 \arrow[d, "h+2"] \\
        E_2 \arrow[r, "\lambda"]                                        & V_2                 
    \end{tikzcd}
\end{equation}

@@

The assembly function $Q: \Gamma(V) \rightarrow \Gamma(H)$ composites the visual variables in $V$ into an element in $H$. Given a monoid action on a set in $V$, there should be a monoid action on the corresponding $Q(\Gamma(V))$.

Lets call $\Gamma(V) = X$ and $Q(\Gamma(V))$

For each region $s$ in the display space $H$, the mark  \cite{bertinIIPropertiesGraphic2011,carpendaleVisualRepresentationSemiology} it belongs to can be found by mapping $s$ back to $K$ via the lookup on $S$ then taking $\xi(s)$ back to a point on $k \in K$ which lies on the path connected component $J \subset K$. 
\begin{equation}
    \begin{tikzcd}
        H \arrow[r, shift left] & S \arrow[l, "\rho(\xi^{-1}(J))", shift left] \arrow[rr, "\xi(s)", shift left] &  & J_{k} =  \{j \in K| \exists \gamma \text{ s.t. } \gamma(0)=k \text{ and }\gamma(1)=j\} \arrow[ll, "\xi^{-1}(J)", shift left]
    \end{tikzcd}
    \label{eq:mark}
\end{equation}
where $\gamma$ is a path where input is a point on the interval [0,1] and

To get back to the display space $H$ from $J$, the inverse image of $J \in S, \xi^{-1}(J)$ is pushed back to $S$, and then $\rho(\xi^{-1}(J))$ maps it into $R^{7}$ such that $Q\circ\xi^*\mu(\xi^{-1}(J))$ generates a graphical mark.

%%abs: R \rightarrow R^+, 
%%f: R \rightarrow R, 
%%abs:[real->real] -> [real->real+]
%%fmap?, fmap(abs)->ufunc on all functions
%%lifting: decorator that only looks at arguments

Q goes from one to the other, could need more information than just the return values... map on global sections means I might need to know the whole section, map V to H says I only need to know points, restrict to the case where defined on the stalk..but will look at particular cases - sections to sections is most general case that is true, but can be defined V to H or or O(V) to O(H) depending on the visualization.

>>>>

\paragraph{Example: Translation}
\textbf{fairly certain I lost the thread here}
According to Stevens, interval data is a set with general linear group actions \cite{stevensTheoryScalesMeasurement1946,leaFormalizationMeasurementScale}. Position is a visual variable that can support translation \cite{bertinIIPropertiesGraphic2011,krygierMakingMapsVisual2005,munznerMarksChannels}.

For example, here $\nu$ is a direct map $\nu(\tau_{i,k}) = \mu{i,k}$ and the transform function is a multiplicative shift $t(x) = x + x$ applied twice

\begin{align}
    \nu(t(t(\tau_{i,k}))) &= t(t(\nu(\tau_{i,k})))\\
    \nu(t(2\tau_{i,k})) &= t(t_v(\mu_{i,k}))\\
    \nu(2\tau_{i,k} + 2\tau_{i,k}) &= t(2\mu_{i,k})\\
    \nu(4\tau_{i,k}) &= 2\mu_{i,k} + 2\mu_{i,k} \\
    \nu(4\tau_{i,k})&=4\mu_{i,k}\\
    4\mu_{i,k}&=4\mu_{i,k}\\
\end{align}
$\nu$ is valid because scaling the data by a factor of 4 causes a scaling of the equivalent visualization by 4, which since the constant factor can be pulled out means they are equivalent.

\paragraph{Example: Invalid $\nu$}
Given a transform $t(x) = 2*x$, we construct a $\nu$ that always takes data to .5: 
\begin{equation}
    \label{eq:nu_equation_bad}
    \begin{tikzcd}
        E_1 \arrow[r] \arrow[r, "\lambda:e\mapsto.5"] \arrow[d, "2e"'] & V_i \arrow[d, "2v"] \\
        E_1 \arrow[r, "\lambda"]                                        & V_1                 
    \end{tikzcd}
\end{equation}

This $\nu$ is invalid because the graph does not commute for $t$:
\begin{align}
    \nu(t(e)) & \overset{?}{=} t(\nu(e))\\
    .5 & \overset{?}{=} t(.5)\\
    .5 & \neq 2*.5
\end{align}

To consutruct a valid $\nu$, the diagram must commute for all monoid actions on the sets $E_i, V_i$.

@@

The assembly function $Q: \Gamma(V) \rightarrow \Gamma(H)$ composites the visual variables in $V$ into an element in $H$. Given a monoid action on a set in $V$, there should be a monoid action on the corresponding $Q(\Gamma(V))$. While $\Gamma(V)$ holds for all cases, we can specialize to the bundle $V$ or the sheaf $\mathcal(V)$ depending on the specific visualization.

\paragraph{Proposition}
If $\forall g \in M$ and $\forall x_1, x_2 \in \Gamma(V)$ then  $Q(x_1) = Q(x_2) \\implies Q(g\circ x_1) = Q(g\circ x_2)$; therefore we can define a group action on $Q(\Gamma(V))=Y$ as $g \circ y = y'$ where $y' = Q(g\circ x)$ with $x \in f^{-1}(y)$

For each region $s$ in the display space $H$, the mark  \cite{bertinIIPropertiesGraphic2011,carpendaleVisualRepresentationSemiology} it belongs to can be found by mapping $s$ back to $K$ via the lookup on $S$ then taking $\xi(s)$ back to a point on $k \in K$ which lies on the path connected component $J \subset K$. 
\begin{equation}
    \begin{tikzcd}
        H \arrow[r, shift left] & S \arrow[l, "\rho(\xi^{-1}(J))", shift left] \arrow[rr, "\xi(s)", shift left] &  & J_{k} =  \{j \in K \text{ s. t. } \exists \gamma \text{ s.t. } \gamma(0)=k \text{ and }\gamma(1)=j\} \arrow[ll, "\xi^{-1}(J)", shift left]
    \end{tikzcd}
    \label{eq:mark}
\end{equation}
where the path\cite{ConnectedSpace2020}  $\gamma$ from $k$ to $j$ is a continous function from the interval [0,1]. To get back to the display space $H$ from $J$, the inverse image of $J \in S, \xi^{-1}(J)$ is pushed back to $S$, and then $\rho(\xi^{-1}(J))$ maps it into $R^{7}$ such that $Q\circ\xi^*\mu(\xi^{-1}(J))$ generates a graphical mark.

### 2021-01-06 draft/sections/visual.tex
q

\documentclass[../main.tex]{subfiles}
\begin{document}
\subsubsection{Marks}
Bertin describes a location on the plane as the signifying characteristic of a point, measurable length as the signifying characteristic of a line, and measurable size as the signifying characteristic of an area and that in display (pixel) space are the point, line, and area marks \cite{bertinIIPropertiesGraphic2011,carpendaleVisualRepresentationSemiology}. For each region $s$ in the display space $H$, the mark it belongs to can be found by mapping $s$ back to $K$ via the lookup on $S$ then taking $\xi(s)$ back to a point on $k \in K$ which lies on the connected component $J \subset K$. 
\begin{equation}
\begin{tikzcd}
    H \arrow[r, shift left] & S \arrow[l, "\rho(\xi^{-1}(J))", shift left] \arrow[rr, "\xi(s)", shift left] &  & J_{k} =  \{j \in K| \exists \Gamma \text{ s.t. } \Gamma(0)=k \text{ and }\Gamma(1)=j\} \arrow[ll, "\xi^{-1}(J)", shift left]
\end{tikzcd}
\label{eq:mark}
\end{equation}
To got back to the display space $H$  from the simplacial complex $J$ of the signifier implanted in the mark, the inverse image of $J \in S, \xi^{-1}(J)$ is pushed back to $S$, and then  $\rho(\xi^{-1}(J))$ maps it into $R^{7}$.

\subsubsection{Visual Idioms: Equivalance class of artists}
n $O(E)$ of the same type, they output the same type of prerender $O(H)$:

Natural transformation + composition is partial ordering? Back and forth is equivalent 
\end{document}

>>>>

\documentclass[../main.tex]{subfiles}
\begin{document}

\end{document}
